---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

Some new line of code

```{r}
4^10
```


This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.


Record all the steps used to process the data and save the raw data. Using R is a good way to record all of the steps since we can keep all the scripts we used, and it is free so that everyone can get access to the program. Adding a comment line at the beginning of every program makes communication between different users much more manageable.  Besides, we will not change the raw data processing in R. Therefore, using R or other programming tools keeps raw data safe.


3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
sqrt(4^13)
```

4) Push this homework to the GitHub repository for the homework. 





